### 2019-06-09 doc/chapters/introduction.tex
added label
text

\section{Overview of Bitcoin-S}
\label{sec:bitcoin_s}

In the work we verify some fragments of the code of Bitcoin-S.
Bitcoin-S is an open source Scala implementation of the Bitcoin protocol. 
There are different projects belonging to Bitcoin-S.
Protocol data structures are defined in the package \textbf{bitcoin-s-core}.
This package is the main target to be verified because it specifies the base of Bitcoin protocol, and it is crucial for correct protocol functionality.
There is also the package \textbf{bitcoind-rpc} which is an RPC client implementation to communicate with \textit{bitcoind}, daemon of Bitcoin Core running on a machine.
Developers of Bitcoin-S are working on the implementation of a lightweight bitcoin client in the package \textbf{bitcoin-s-spv-node}.
The whole list of packages can be found on GitHub in the \href{https://github.com/bitcoin-s}{organization Bitcoin-S}.

Bitcoin-S is a large project implementing many functionalities.
In this work one of them is going to be examined and worked on, namely the property of the Bitcoin that a non-coinbase transaction can not generate new coins.
Thus, the code of Bitcoin-S should be analyzed, and fragments implementing this feature should be identified.
Afterwards, the fragments should be rewritten, so that Stainless can accept it.
After that a formal specification for functions should be defined and annotated according Stainless libraries, so that Stainless can verify correctness of the code.

@@

\subsection{No Inflation Property}

\subsection{Addition with Zero Property}

>>>>

@@

Bitcoin-S is a large project found on GitHub implementing many functionalities.
In this work two of them is going to be examined and worked on, namely the \nameref{property_1} and the \nameref{property_2} describer shortly.
Thus, we go through the relevant code parts to verify those properties, look at some challenges with Stainless and see why we should write software with verification in mind.
We will rewrite the code to Pure Scala, because Bitcoin-S is not written in it.

\subsection{No Inflation Property}
\label{property_1}

\subsection{Addition with Zero Property}
\label{property_2}
